\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2025-06-24 extra/paper_original.tex
Move data files to extra

In terms of model error, some data points show high error (see
Figure~\ref{fig-nldervisMNISTPACMAP}) due to their deviation from the
typical high-D data structure, acting as outliers. This is evident when
comparing the images associated with these high model error points (see
Figure~\ref{fig-sampleimgerror}) to others (see
Figure~\ref{fig-sampleimg}).

>>>>

There are certain data points that exhibit high error rates due to their
deviation from the usual high-dimensional data structure, which makes
them outliers. These outliers can be classified into two types: those
that are outliers within the nonlinear structure and those that lie
outside of it. The images associated with high model error points within
the nonlinear structure display different patterns of the digit 1, as
shown in Figure~\ref{fig-sampleimgerrorwithin}. However, when comparing
these images to the ones found outside of the nonlinear structure, it
becomes evident that the latter display different patterns of the digit
1 (see Figure~\ref{fig-sampleimgerror}).
Figure~\ref{fig-nldervisMNISTPACMAP} shows some data points that have
high error rates due to their outlier status.
